Putting Species into Quantiles
==============================

Divide the range sizes from 0 to 1 by .2 or 20%

```{r eval=F}
quantile(barone.ranges$range, seq(0, 1, by=.2))
```

## Determine the number of species in each quantile

Use the sum function to total the number of species between the range given.
The range given is determine by the quantile splits of the data.

```{r eval=F}
sum(barone.ranges$range<=500)
sum(barone.ranges$range>500 & barone.ranges$range<=734)
sum(barone.ranges$range>734 & barone.ranges$range<=848)
sum(barone.ranges$range>848 & barone.ranges$range<=950)
sum(barone.ranges$range>950)
```

## Assign species to quantiles in the original csv file

Create a new blank column called Quantile

```{r eval=F}
barone.ranges$Quantile=NA
```
If the value in column range of barone.ranges meets the criteria stated,
place the quantile name in column Quantile

```{r eval=F}
barone.ranges$Quantile[barone.ranges$range<=500]="Q1"
barone.ranges$Quantile[barone.ranges$range>500 & barone.ranges$range<=734]="Q2"
barone.ranges$Quantile[barone.ranges$range>734 & barone.ranges$range<=848]="Q3"
barone.ranges$Quantile[barone.ranges$range>848 & barone.ranges$range<=950]="Q4"
barone.ranges$Quantile[barone.ranges$range>950]="Q5"
```

## Assign species to quantile in the original csv file that includes abundance

Create a new blank column called Quantile

```{r eval=F}
Sonadora$Quantile=NA
```

Change the SpeciesCode column to all uppercase so that the two csv files match

Create a new blank column called Quantile

```{r eval=F}
barone.ranges$SpeciesCode=toupper(barone.ranges$SpeciesCode)
```

Get a list of the species that are in Q1.
Repeat for Q2-Q5.

```{r eval=F}
Q1=list(barone.ranges$SpeciesCode[barone.ranges$range<=500])
```

Add Q1-Q5 for each of these species to the Quantile column
**Had to do this 119 times, once for each species because I couldn't figure out
how to match/subset/anything with a list of the names**

```{r eval=F}
Sonadora$Quantile[Sonadora$stemSpeciesCode=="ALCFLO"]="Q1"
```

